---
title: "Demographic data analysis. ANCOVA analysis"
date: "2023-07-31"

---


```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(tidyverse)
library(ggpubr)
library(rstatix)
library(broom)
library(readxl)
library(gtsummary)
```


One-way ANCOVA with age as covariate
https://www.datanovia.com/en/lessons/ancova-in-r/

```{r}
#Load data

slope <-
  read_xlsx("", sheet = "")

offset <-
  read_xlsx("", sheet = "")

iaf <-read_xlsx("", sheet = "" )

power <-read_xlsx("", sheet = "" )

demographic <-read_xlsx("")
```


```{r}
#add age 
# Merge 'slope' dataframe with 'age' based on 'id'
slope <- merge(slope, demographic, by = "id", all.x = TRUE)

offset <- merge(offset, demographic, by = "id", all.x = TRUE)

iaf <- merge(iaf, demographic, by = "id", all.x = TRUE)

power <- merge(power, demographic, by = "id", all.x = TRUE)

```

**REMOVED SUBJECTS:**

```{r}
#remove subjects

# List of IDs to remove
ids_to_remove <- c(236, 32, 107, 113, 221, 13, 118, 122)

# Remove rows for the specified IDs in each dataset
slope <- slope[!(slope$id %in% ids_to_remove) & !(slope$group == "M"), ]
offset <- offset[!(offset$id %in% ids_to_remove) & !(offset$group == "M"), ]
iaf <- iaf[!(iaf$id %in% ids_to_remove) & !(iaf$group == "M"), ]
power <- power[!(power$id %in% ids_to_remove) & !(power$group == "M"), ]

# Check if all datasets have equal number of rows
num_rows <- nrow(slope)
if (nrow(offset) != num_rows || nrow(iaf) != num_rows || nrow(power) != num_rows) {
  print("Warning: Datasets do not have an equal number of rows.")
}

```



```{r}
# Define the desired order of levels
desired_order <- c("NCF", "NCL", "OC", "IUD")


# Function to convert group names to factors and reorder levels
convert_and_reorder <- function(df) {
  df$group <- factor(df$group, levels = desired_order)
  return(df)
}

# Apply the conversion and reordering to all datasets
slope <- convert_and_reorder(slope)
offset <- convert_and_reorder(offset)
iaf <- convert_and_reorder(iaf)
power <- convert_and_reorder(power)
```

```{r}
write_csv(slope, file ="./data/slope_merge.csv" )
write_csv(iaf, file ="./data/iaf_merge.csv" )
write_csv(power, file ="./data/power_merge.csv" )
```



```{r}
slope |> 
  summarise(mean_age = mean(age),
            sd_age   = sd(age))
```

# **demographic table**
```{r}
Datatabledemo<-select(iaf, c(age, Progesterone, Estradiol, Testosterone, group))

tbl_summary_1 <- Datatabledemo %>%
  tbl_summary(
    by = group,
    missing = "no",
    statistic = list(
      all_continuous() ~ "{mean} ({sd})"))%>%
  add_p(test = all_continuous() ~ "aov",
        pvalue_fun = function(x) style_pvalue(x, digits = 2))
tbl_summary_1
```
**ANOVA for age**
```{r}
Age_anova <- aov(age ~ group, data = iaf)
summary(Age_anova)
# Perform Tukey's HSD post-hoc test
TukeyHSD(Age_anova)
# Perform pairwise comparisons with Bonferroni correction
pairwise.t.test(iaf$age, iaf$group, p.adj = "bonferroni")
```


```{r}
partial_eta_squared(Age_anova)
```

**ANOVA for Progesterone**
```{r}
Progesterone_anova <- aov(Progesterone ~ group, data = iaf)
summary(Progesterone_anova)
# Perform Tukey's HSD post-hoc test
TukeyHSD(Progesterone_anova)
# Perform pairwise comparisons with Bonferroni correction
pairwise.t.test(iaf$Progesterone, iaf$group, p.adj = "bonferroni")
```


```{r}
partial_eta_squared(Progesterone_anova)
```
**ANOVA for Testosterone**
```{r}
testos_anova <- aov(Testosterone ~ group, data = iaf)
summary(testos_anova)
# Perform Tukey's HSD post-hoc test
TukeyHSD(testos_anova)
# Perform pairwise comparisons with Bonferroni correction
pairwise.t.test(iaf$Testosterone, iaf$group, p.adj = "bonferroni")
```
```{r}
partial_eta_squared(testos_anova)
```
# **SLOPE**

**PARAMETERS BETWEEN GROUPS: TABLE**
```{r}
print(slope %>% group_by(group) %>% get_summary_stats(median_slope, type = "median_iqr"))
```





```{r}
slope.png <- ggplot(slope,aes(x = group, y = median_slope, fill = group)) +
geom_violin(width = 1) +
geom_boxplot(width = 0.1, color = "black", alpha = 0.2) +
geom_jitter(width = 0.2, height = 0, alpha = 0.5, color = "black") +
labs(x = " ") +
ylab("1/f Slope (γ)") +
scale_fill_manual(values = c("#009E73","#E69F00", "#0072B2", "#CC79A7"))+
theme_classic() +
theme(axis.text = element_text(size = 14), legend.position = "none") +
font("axis.title", size = 18)

slope.png

ggsave("slope.png.png", slope.png, width = 5.33,
  height = 3.6) 
```


##  **CHECK ASSUMPTIONS**



1. **Linearity assumption**

```{r}
ggscatter(
  slope, x = "age", y = "median_slope",
  color = "group", add = "reg.line"
  )+
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~"), color = group)
    )
```

2. **Homogeneity of regression slopes**

```{r}
slope %>% anova_test(median_slope ~ group*age)
```


3. **Normality of residuals**
```{r}
# Fit the model, the covariate goes first
model <- lm(median_slope ~ age + group, data = slope)
# Inspect the model diagnostic metrics
model.metrics <- augment(model) %>%
  select(-.hat, -.sigma, -.fitted) # Remove details
head(model.metrics, 3)
```

```{r}
# Assess normality of residuals using shapiro wilk test
shapiro_test(model.metrics$.resid)
```


4. **Homogeneity of variances**

```{r}
model.metrics %>% levene_test(.resid ~ group)
```


5. **Outliers**

```{r}
model.metrics %>% 
  filter(abs(.std.resid) > 3) %>%
  as.data.frame()
```


## **ANCOVA**
```{r}
res.aov <- slope %>% anova_test(median_slope ~ age + group)
get_anova_table(res.aov)

```



# **IAF**

**PARAMETERS BETWEEN GROUPS: TABLE**
```{r}
print(iaf %>% group_by(group) %>% get_summary_stats(median_iaf, type = "median_iqr"))
```


**GRAPHS**


```{r}
ggplot(iaf,aes(x = group, y = median_iaf, fill = group)) +
  geom_violin(width = 1) +
  geom_boxplot(width = 0.1, color = "black", alpha = 0.2) +
  geom_jitter(width = 0.2, height = 0, alpha = 0.5, color = "black") +
  labs(x = " ") +
  ylab("IAF (Hz)") +
  scale_fill_manual(values = c("#009E73","#E69F00", "#0072B2", "#CC79A7"))+
  theme_classic() +
  theme(axis.text = element_text(size = 14), legend.position = "none") +
  font("axis.title", size = 18)
```


##  **CHECK ASSUMPTIONS**

1. **Linearity assumption**

```{r}
ggscatter(
  iaf, x = "age", y = "median_iaf",
  color = "group", add = "reg.line"
  )+
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~"), color = group)
    )
```

2. **Homogeneity of regression slopes**

```{r}
iaf %>% anova_test(median_iaf ~ group*age)
```

3. **Normality of residuals**
```{r}
# Fit the model, the covariate goes first
model <- lm(median_iaf ~ age + group, data = iaf)
# Inspect the model diagnostic metrics
model.metrics <- augment(model) %>%
  select(-.hat, -.sigma, -.fitted) # Remove details
head(model.metrics, 3)
```

```{r}
# Assess normality of residuals using shapiro wilk test
shapiro_test(model.metrics$.resid)
```

4. **Homogeneity of variances**

```{r}
model.metrics %>% levene_test(.resid ~ group)
```

5. **Outliers**

```{r}
model.metrics %>% 
  filter(abs(.std.resid) > 3) %>%
  as.data.frame()
```

## **ANCOVA**
```{r}
iaf_res.aov <- iaf %>% anova_test(median_iaf ~ age + group)
get_anova_table(iaf_res.aov)

```



# **POWER**

```{r}
power$median_power_log <- log(power$median_power)
```


**PARAMETERS BETWEEN GROUPS: TABLE**
```{r}
print(power %>% group_by(group) %>% get_summary_stats(median_power, type = "median_iqr"))
```


**GRAPHS**


```{r}
ggplot(power, aes(x = group, y = median_power_log, fill = group)) +
  geom_violin(width = 1) +
  geom_boxplot(width = 0.1, color = "black", alpha = 0.2) +
  geom_jitter(width = 0.2, height = 0, alpha = 0.5, color = "black") +
  labs(x = "") +
  ylab("log Alpha Power (µV2)") +
  scale_fill_manual(values = c("#009E73","#E69F00", "#0072B2", "#CC79A7"))+
  theme_classic() +
  theme(axis.text = element_text(size = 14), legend.position = "none") +
  font("axis.title", size = 18) +
  coord_cartesian(ylim = c(-2.5, 5))  
  powerLog


```


##  **CHECK ASSUMPTIONS**

1. **Linearity assumption**

```{r}
ggscatter(
  power, x = "age", y = "median_power_log",
  color = "group", add = "reg.line"
  )+
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~"), color = group)
    )
```

2. **Homogeneity of regression slopes**

```{r}
power %>% anova_test(median_power_log ~ group*age)
```

3. **Normality of residuals**
```{r}
# Fit the model, the covariate goes first
model <- lm(median_power_log ~ age + group, data = power)
# Inspect the model diagnostic metrics
model.metrics <- augment(model) %>%
  select(-.hat, -.sigma, -.fitted) # Remove details
head(model.metrics, 3)
```

```{r}
# Assess normality of residuals using shapiro wilk test
shapiro_test(model.metrics$.resid)
```

4. **Homogeneity of variances**

```{r}
model.metrics %>% levene_test(.resid ~ group)
```

5. **Outliers**

```{r}
model.metrics %>% 
  filter(abs(.std.resid) > 3) %>%
  as.data.frame()
```

## **ANCOVA**
```{r}
power_res.aov <- power %>% anova_test(median_power_log ~ age + group)
get_anova_table(power_res.aov)

```

